UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-16 files/paper/tex/methodology.tex
update

\subsection{Dataset Generation}
Depth, lighting conditions, camera model, and physical location in the underwater environment are all factors that affect the 
amount of distortion an image will be subjected to. Under certain conditions, it is possible that an underwater image may have 
very little distortion, or none at all. To generate the dataset to train the generative model\starnote{check this please}, we let 
$I^C$ be an underwater image with no distortion, and $I^D$ be the same image with distortion. Our goal is to learn the function 
$f: I^D \rightarrow I^C$. Becasue of the difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, 
but never both.

To circumvent the problem of insufficient image data in $I^D$, we use CycleGAN to generate $I^D$ from $I^C$, which gives us a 
paired dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping $F: X 
\rightarrow Y$. Figure~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a 
generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process, CycleGAN 
simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In Section~\ref{sec:experiments}, we compare images 
generated by CycleGAN with images generated through our approach.

\subsection{Adversarial Networks}
\starnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
(GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
competes against an adversary. From a classification perspective, the generator network produces instances which actively attempts 
to `mislead' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
instances and the `false' but realistic looking instances produced by the generator network, and thus improve its classification 
accuracy. In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and confuse the 
discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original GAN 
formulation, our goal is to solve the minimax problem:

@@

Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, 
the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead to issues 
such as the vanish gradient and mode collapse~\starnote{Clarify?}. There have been a number of recent methods which hypothesize a 
different loss function for the discriminator
\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
constraint on the gradient norm of the discriminator's output with respect to its input. Following
\cite{gulrajani2017improved}, our new objective then becomes

@@

\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}

>>>>

\subsection{Dataset Generation}
Depth, lighting conditions, camera model, and physical location in the underwater environment are all factors that affect the 
amount of distortion an image will be subjected to. Under certain conditions, it is possible that an underwater image may have 
very little distortion, or none at all. We let 
$I^C$ be an underwater image with no distortion, and $I^D$ be the same image with distortion. Our goal is to learn the function 
$f: I^D \rightarrow I^C$. Becasue of the difficulty of collecting underwater data, more often than not only $I^D$ or $I^C$ exist, 
but never both.

To circumvent the problem of insufficient image pairs, we use CycleGAN to generate $I^D$ from $I^C$, which gives us a 
paired dataset of images. Given two datasets $X$ and $Y$, where $I^C \in X$ and $I^D \in Y$, CycleGAN learns a mapping $F: X 
\rightarrow Y$. Figure~\ref{fig:cgan_samples} shows paired samples generated from CycleGAN. From this paired dataset we train a 
generator $G$ to learn the function $f: I^D \rightarrow I^C$. It should be noted that during our data generation process, CycleGAN 
simultaneously learns a mapping $G: Y \rightarrow X$, which is similar to $f$. In Section~\ref{sec:experiments}, we compare images 
generated by CycleGAN with images generated through our approach.

\subsection{Adversarial Networks}
\starnote{check this paragraph as I added some more text}In machine learning literature, Generative Adversarial Networks 
(GANs)~\cite{goodfellow2014generative} represent a class of generative models based on game theory in which a generator network 
competes against an adversary. From a classification perspective, the generator network produces instances which actively attempt 
to `fool' the discriminator network. The goal is for the discriminator network to be able to distinguish between `true' 
instances coming from the dataset and `false' instances produced by the generator network.
%, and thus improve its classification accuracy.
In our case, conditioned on an image $I^D$, the generator is trained to produce an image to try and fool the 
discriminator, which is trained to distinguish between distorted and non-distorted underwater images. In the original
GAN formulation, our goal is to solve the minimax problem:

@@

Note for simplicity in notation, we will further omit $I^C \sim p_{train}$ and $I^D \sim p_{gen}$. In this formulation, 
the discriminator is hypothesized as a classifier with a sigmoid cross-entropy loss function, which in practice may lead
to issues  such as the vanish gradient and mode collapse. As shown by \cite{arjovsky2017towards}, as
the discriminator improves, the gradient of the generator vanishes, making it difficult or impossible to train. Mode
collapse occurs when the generator ``collapses'' onto a single point, fooling the discriminator with only one instance
\starnote{Such as when you are training a GAN to generate digits from MNIST, but it only generates a 7, when in reality
you'd want it to generate a diverse amount of all the digits. Not sure if we should expand more.}.
There have been a number of recent methods which hypothesize a different loss function for the discriminator
\cite{mao2016least,arjovsky2017wasserstein,gulrajani2017improved,zhao2016energy}. We focus on the Wasserstein GAN
(WGAN) \cite{arjovsky2017wasserstein} formulation, which proposes to use the Earth-Mover or \textit{Wasserstein-1}
distance $W$ by constructing a value function using the Kantorovich-Rubinstein duality \cite{villani2008optimal}.
In this formulation, $W$ is approximated given a set of $k$-Lipschitz functions $f$ modeled as neural networks. To
ensure $f$ is $k$-Lipschitz, the weights of the discriminator are clipped to some range $[-c, c]$. In our work, we
adopt the Wasserstein GAN with gradient penalty (WGAN-GP) \cite{gulrajani2017improved}, which instead of clipping
network weights like in \cite{arjovsky2017wasserstein}, ensures the Lipschitz constraint by enforcing a soft
constraint on the gradient norm of the discriminator's output with respect to its input. Following
\cite{gulrajani2017improved}, our new objective then becomes

@@

\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
%\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}
